---
title: "DATA 607 HW12"
author: "Christina Kasman"
date: "11/16/2017"
output: html_document
---

```{r}
library(rmarkdown)
library(RMySQL)
library(RNeo4j)
drv <- dbDriver("MySQL")
```


```{r, echo=FALSE}
con <- dbConnect(drv, user = "root", password = "barney17", dbname = "TB", host = "localhost")
```

con <- dbConnect(drv, user = "root", password = "xxxx", dbname = "TB", host = "localhost")

```{r}
dbListFields(con, "tb")
```

```{r}
#Adjust for candidate type and location
query <- "SELECT * FROM tb;"
tb <- dbGetQuery(con, query)
```

```{r, echo=FALSE}
graph <- startGraph("http://localhost:7474/db/data/", 
                    username="neo4j", 
                    password="barney17")
```
graph <- startGraph("http://localhost:7474/db/data/", 
                    username="neo4j", 
                    password="xxxx")
```{r}
clear(graph, input = FALSE)
```


Pros of storing in NoSQL
1. Easier to save data across databases
2. Easier to update records
3. More agile
4. Not in tabular format
5.Elastic scalability


Pros of Relational Databases
1.More mature
2. More advanced expertise - been around longer
3. Tabular structure
4. Ease of data retrieval
5. Use generical language (SQL)


