---
title: "DATA 607 HW 5"
author: "Christina Kasman"
date: "10/1/2017"
output:
  html_document: default
  pdf_document: default
---
<h3>(1) Create a .CSV file (or optionally, a MySQL database!) that includes all of the information above.
You’re encouraged to use a “wide” structure similar to how the information appears above, so
that you can practice tidying and transformations as described below.
(2) Read the information from your .CSV file into R, and use tidyr and dplyr as needed to tidy
and transform your data.
(3) Perform analysis to compare the arrival delays for the two airlines.
<h3>

Load libraries
```{r}
library(dplyr)
library(tidyr)
```

Read CSV file
Rename Columns
```{r}
airplanes <-read.csv("/Users/christinakasman/Desktop/airplanes data607.csv", header=TRUE, sep=",", stringsAsFactors=FALSE)
airplanes
```

```{r}
names(airplanes) <- c("Airline", "Status", "LosAngeles", "Phoenix", "SanDiego", "SanFrancisco", "Seattle")
airplanes
```

Remove NA values using drop_na from plyr package
```{r}
airplanes5 <- airplanes %>% drop_na()
airplanes5
```


```{r}
for (i in 1:dim(airplanes5)[1]){
  if (i %% 2 == 0){
      airplanes5$Airline[i] <-  airplanes5$Airline[i-1]
  }
}
airplanes5
```


Use gather function to transform data into Tidy dataset
```{r}
airplanesnew <- airplanes5%>% gather("city", "Count", LosAngeles:Seattle) 
airplanesnew
```

```{r}
airplanesnew2 <- as.data.frame(airplanesnew)
airplanesnew4 <- airplanesnew %>%  
  spread("Status", "Count")
names(airplanesnew4) <- c("Airline", "city", "Delayed", "Ontime")
airplanesnew4
```
```{r}
counts <- airplanesnew4 %>% group_by(Airline) %>% summarise(Totaldelayed = sum(Delayed), Totalontime = sum(Ontime))
counts
```
```{r}
graph1 <- mutate(counts, Airline, Totaldelayed, Totalontime, Totalflights = Totaldelayed + Totalontime, percentdelayed = ((Totaldelayed/(Totalontime + Totaldelayed))*100), percentontime = ((Totalontime/(Totalontime + Totaldelayed))*100))
graph1
```

**Overall, AM West has a nigher number of delayed flights, but when looking at ratios, Alaska has the highest probability of having a flight delayed. AM West has almost double the total number of flights**


```{r}
library(ggplot2)
g <- ggplot(graph1, aes(x = Airline)) + geom_bar(aes(weight = Totaldelayed), fill="#DD8888") + ylab("Delayed") + ggtitle("Total Delayed Flights per Airline")
g
```


```{r}
graph2 <- airplanesnew4 %>% group_by(Airline, city) %>% summarise(Totaldelayed = sum(Delayed), Totalontime = sum(Ontime)) %>% 
 mutate(city, Totaldelayed, Totalontime, percentdelayed = ((Totaldelayed/(Totalontime + Totaldelayed))*100), percentontime = ((Totalontime/(Totalontime + Totaldelayed))*100))
graph2
```
```{r}
g3 <- ggplot(graph2, aes(x = city, y = Totaldelayed)) + geom_bar(aes(fill= Airline), stat = "Identity", position=position_dodge()) + ylab("Delayed") + ggtitle("Total Delayed Flights per Airline")
g3
```

**The highest number of delayed flights occur at Phoenix aiport by AM West Airlines** 
```{r}
g1 <- ggplot(graph2, aes(x = city, y = percentdelayed)) + geom_bar(aes(fill= Airline), stat = "Identity", position=position_dodge()) + ylab("On Time") + ggtitle("Percent Delayed Flights per Airline")
g1
```

**The highest probability of flights delayed occur at San Francisco airport by AM West**



