---
title: "HW 2 DATA 607"
author: "Christina Kasman"
date: "9/10/2017"
output:
  html_document: default
  pdf_document: default
---
Assignment:
Choose six recent popular movies. Ask at least five people that you know (friends, family, classmates,imaginary friends) to rate each of these movie that they have seen on a scale of 1 to 5. Take the results (observations) and store them in a SQL database. Load the information into an R dataframe.
#I decided to choose 10 movies instead of 6 to create additional data

```{r}
#Connect to SQL Database 
library(RMySQL)
drv <- dbDriver("MySQL")
```
```{r, echo=FALSE}
con <- dbConnect(drv, user = "root", password = "barney17", dbname = "moviedata", host = "localhost")
```

con <- dbConnect(drv, user = "root", password = "password", dbname = "moviedata", host = "localhost")

```{r}
dbListFields(con, "moviedata")
query <- "SELECT * FROM moviedata;"
moviedata <- dbGetQuery(con, query)
```
```{r}
dbDisconnect(con)
#save as dataframe
completemoviedata <- as.data.frame(moviedata)
completemoviedata
```
```{r}
#Create boxplot to show average movie ratings
library(ggplot2)
ggplot(completemoviedata, aes(movie,rating)) + 
  geom_boxplot() + 
  ylab("Rating") + theme(axis.text.x = element_text(angle = 90, hjust = 1))+ ggtitle("Average Ratings for Movies")
```

