---
title: "HW 3 DATA 607"
author: "Christina Kasman"
date: "9/15/2017"
output: html_document
---
```{r}
library(stringr)
```

```{r}
raw.data <-" 555-1239Moe Szyslak( 636) 555-0113Burns, C. Montgomery555 -6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
```
Question 1
```{R}
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name
```

```{r}
split_name <- str_split(name, ",")
split_name
```
str_
```{r}
split_name <- data.frame(split_name)
split_name
```
```{r}
ln <- data.frame(split_name[1,])
fn <- data.frame(split_name[2, ])
split_name <- ifelse(fn == ln, ln , rbind(fn, ln))
split_name
```
Question 2:
Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.).

```{r}
title <- str_detect(name, "[[:alpha:]]{2,}\\.")
title
```
Construct a logical vector indicating whether a character has a second name.

```{r}
secondname <- str_detect(name, "[A-Z]\\.{1}")
secondname
```
Describe the types of strings that conform to the following regular expressions and construct an example that is matched by the regular expression. 

[0-9] +\\ $ 
Matches numbers 0-9 zero or more times with a dollar sign following the number string
```{r}
example <- "6729$"  
regex = "[0-9]+\\$"
str_extract(example, regex)
```



\\ b[ a-z]{ 1,4}\\ b
matches character a-z atleast 1 time and at most 4 times with empty string at either edge of the word
```{r}
 example <- "abcd efgh"  
regex = "\\b[a-z]{1,4}\\b"
str_extract(example, regex)
```

.*?\\. txt $
matches a string followed by .txt 
```{r}
example <- "abcd.txt"  
regex = ".*?\\.txt$"
str_extract(example, regex)
```


\\ d{ 2}/\\ d{ 2}/\\ d{ 4} 
matches dates with two digit month, two digit day, and four digit year sepreated by \
```{r}
example <- "01/17/19889"  
regex = "\\d{2}/\\d{2}/\\d{4}"
str_extract(example, regex)
```

<(. +?) >. +? </\\ 1 >
matches an HTML tag
```{r}
example = "<Title>Sometext</head><body>Sometext</body>"
regex = "<(.+?)>.+?</\\1>" 
str_extract(example, regex) 
```

